High-level cognition during story listening is reflected in high-order dynamic correlations in neural activity patterns

### 2021-06-10 paper/main.tex
updated description of how we normalized the decoding accuracies in fig 4

\begin{figure}[tp]
  \centering
  \includegraphics[width=\textwidth]{figs/decode_level}
  \caption{\textbf{Across-participant timepoint decoding accuracy varies with
      correlation order and cognitive engagement.}
    \textbf{a.~Decoding accuracy as a function of order: PCA.}
    \textit{Order} ($x$-axis) refers to the maximum order of dynamic
    correlations that were available to the classifiers (see
    \textit{Feature weighting and testing}).  The reported
    across-participant decoding accuracies are averaged over all
    kernel shapes and widths (see \textit{Identifying robust decoding
      results}).  The $y$-values are displayed relative to chance
    accuracy (intact: $\frac{1}{300}$; paragraph: $\frac{1}{272}$;
    word: $\frac{1}{300}$; rest: $\frac{1}{400}$; these chance accuracies
    were subtracted from the observed accuracies to obtain the
    relative accuracies reported on the $y$-axis).  The error ribbons
    denote 95\% confidence intervals across cross-validation folds
    (i.e., random assignments of participants to the training and test
    sets).  The colors denote the experimental condition.  Arrows
    denote sets of features that yielded reliably higher (upward
    facing) or lower (downward facing) decoding accuracy than the mean
    of all other features (via a two-tailed $t$-test, thresholded at
    $p < 0.05$).  Figure~\ref{fig:ttests} displays additional
    comparisons between the decoding accuracies achieved using
    different sets of neural features.  The circled values represent
    the maximum decoding accuracy within each experimental condition.
    \textbf{b.~Normalized timepoint decoding accuracy as a function of order:
      PCA.}  This panel displays the same results as Panel a, but here
    each curve has been normalized to have a maximum value of 1 and a
    minimum value of 0 (including the upper and lower bounds of the
    respective 95\% confidence intervals).  Panels a and b used PCA to
    project each high-dimensional pattern of dynamic correlations onto
    a lower-dimensional space.  \textbf{c.~Timepoint decoding accuracy as a
      function of order: eigenvector centrality.} This panel is in the
    same format as Panel a, but here eigenvector centrality has been
    used to project the high-dimensional patterns of dynamic
    correlations onto a lower-dimensional space.
    \textbf{d.~Normalized timepoint decoding accuracy as a function of order:
      eigenvector centrality.} This panel is in the same format as
    Panel b, but here eigenvector centrality has been used to project
    the high-dimensional patterns of dynamic correlations onto a
    lower-dimensional space. See Figures~\kernelshape~and~\kernelwidth~for decoding results broken down by kernel shape and width, respectively.}
  \label{fig:decoding}
\end{figure}

>>>>

\begin{figure}[tp]
  \centering
  \includegraphics[width=\textwidth]{figs/decode_level}
  \caption{\textbf{Across-participant timepoint decoding accuracy varies with
      correlation order and cognitive engagement.}
    \textbf{a.~Decoding accuracy as a function of order: PCA.}
    \textit{Order} ($x$-axis) refers to the maximum order of dynamic
    correlations that were available to the classifiers (see
    \textit{Feature weighting and testing}).  The reported
    across-participant decoding accuracies are averaged over all
    kernel shapes and widths (see \textit{Identifying robust decoding
      results}).  The $y$-values are displayed relative to chance
    accuracy (intact: $\frac{1}{300}$; paragraph: $\frac{1}{272}$;
    word: $\frac{1}{300}$; rest: $\frac{1}{400}$; these chance accuracies
    were subtracted from the observed accuracies to obtain the
    relative accuracies reported on the $y$-axis).  The error ribbons
    denote 95\% confidence intervals across cross-validation folds
    (i.e., random assignments of participants to the training and test
    sets).  The colors denote the experimental condition.  Arrows
    denote sets of features that yielded reliably higher (upward
    facing) or lower (downward facing) decoding accuracy than the mean
    of all other features (via a two-tailed $t$-test, thresholded at
    $p < 0.05$).  Figure~\ref{fig:ttests} displays additional
    comparisons between the decoding accuracies achieved using
    different sets of neural features.  The circled values represent
    the maximum decoding accuracy within each experimental condition.
    \textbf{b.~Normalized timepoint decoding accuracy as a function of order:
      PCA.}  This panel displays the same results as Panel a, but here
    each curve has been normalized to be bounded between 0 and 1
    (inclusive) by subtracting the minimum accuracy
    (across all folds and orders) and then dividing by the maximum
    accuracy (again, across all folds and orders).  Panels a and b used PCA to
    project each high-dimensional pattern of dynamic correlations onto
    a lower-dimensional space.  \textbf{c.~Timepoint decoding accuracy as a
      function of order: eigenvector centrality.} This panel is in the
    same format as Panel a, but here eigenvector centrality has been
    used to project the high-dimensional patterns of dynamic
    correlations onto a lower-dimensional space.
    \textbf{d.~Normalized timepoint decoding accuracy as a function of order:
      eigenvector centrality.} This panel is in the same format as
    Panel b, but here eigenvector centrality has been used to project
    the high-dimensional patterns of dynamic correlations onto a
    lower-dimensional space. See Figures~\kernelshape~and~\kernelwidth~for decoding results broken down by kernel shape and width, respectively.}
  \label{fig:decoding}
\end{figure}
